Visualizing demographic evolution using geographically inconsistent census data

### 2019-08-12 paper/method.tex
more fixes, regionalisation ideas
interface change (percentage population)

\subsection{Clusters and trajectories}
While the partition of the data into different clusters helps the user to
understand what groups exist and where they are, we are also interested in the
evolution of these groups. To examine this process of evolution directly, we
introduce the concepts\revision{of \emph{temporal paths} and \emph{trajectories}.

@@

Each aspect is represented by a stacked bar plot, where the width of each
rectangle corresponds to the average percentage of that variable over the
considered period. In this case, about half of the people in Chicago in the
considered period are married, and the percentage that are Widowers or Divorced
is roughly similar. About half of the population work in Administrative jobs, a
third never completed high-school, approximately half have gross family income
below 50,000USD per year. The vast majority identify as white. Placing the mouse
over one of the bars will open a small panel with the temporal evolution of that
specific variable, and clicking on the chevron on the right side expands the
corresponding aspect, showing details of the temporal evolution of each variable
and also the corresponding IQRs for the whole city.

>>>>

\subsection{Clusters and trajectories}
While the partition of the data into different clusters helps the user to
understand what groups exist and where they are, we are also interested in the
evolution of these groups. To examine this process of evolution directly, we
introduce the concepts\revision{ of \emph{temporal paths} and \emph{trajectories}.

@@

Each aspect is represented by a stacked bar plot, where the width of each
rectangle corresponds to \revision{the percentage of population in that variable
over the considered period. In this case, a little less than half of the
population are married, and the percentage that are Widowers or Divorced is
roughly similar. About half of the population work in Administrative jobs, a
third never completed high-school, approximately fourty percentq have gross
family income below 50,000USD per year. About sixty percent identify as white.
Placing the mouse over one of the bars will open a small panel with the temporal
evolution of the population percentage of that specific variable, and clicking
on the chevron on the right side expands the corresponding aspect, showing
census level statistics, with details of the temporal evolution of each variable
and also the corresponding IQRs for the whole city. Those values are potentially
different, for instance, while the overall population of this region is about
sixty percent White, it includes regions with wildly different percentages, so
the average percentage of White population over the CTs is a little over fourty
percent.}
